%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}
\usepackage{lmodern}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xifthen}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[3]{
  \item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2}
  \end{tabular*}%
  \ifthenelse{\isempty{#3}}{}{\hspace{-0.25em}\textit{\small #3}}%
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, itemsep=1pt, parsep=0pt, topsep=1pt, partopsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\enlargethispage{2\baselineskip}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Mahesh Chitakoti} \\ \vspace{1pt}
    \small \faPhone\, \href{tel:+919481777227}{+91 94817 77227} $|$
    \faEnvelope\, \href{mailto:maheshchitkoti@gmail.com}{maheshchitkoti@gmail.com} $|$
    \faLinkedin\, \href{https://linkedin.com/in/maheshchitakoti}{LinkedIn} $|$
    \faGithub\, \href{https://github.com/maheshchichkoti}{GitHub}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item \small{AI Engineer and Full Stack Developer with 2.5+ years of experience building production AI systems and scalable web applications. Specialized in RAG pipelines, agentic workflows, and vector search, with a strong backend foundation in Python, FastAPI, Node.js, and cloud-native infrastructure. Recently reduced LLM inference costs by \textbf{35\%} through semantic caching on a production RAG system.}
\end{itemize}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=2pt]
\item{
\textbf{Languages:} Python, JavaScript, TypeScript, SQL \\
\textbf{AI \& GenAI:} RAG, Agentic Workflows, LangChain, LlamaIndex, OpenAI, Gemini, Vector Search, Prompt Engineering \\
\textbf{Backend:} Node.js, Express.js, NestJS, FastAPI, REST APIs, GraphQL, WebSockets, Microservices \\
\textbf{Frontend:} React.js, Next.js, Redux, Tailwind CSS \\
\textbf{Databases:} PostgreSQL, MongoDB, Redis, Qdrant, pgvector \\
\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, GitHub Actions, CI/CD
}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
    {AI Developer -- SAHIONEXT Technology Pvt. Ltd.}{Oct 2025 -- Apr 2026}
    {Remote}{}
    \resumeItemListStart
        \resumeItem{Architected and deployed production \textbf{RAG pipelines} using \textbf{FastAPI, LangChain, Gemini APIs, and Redis semantic caching}, reducing LLM inference costs by \textbf{35\%}.}
        \resumeItem{Developed AI microservices for transcript processing and semantic search over millions of indexed records using \textbf{Qdrant}, tuning embeddings and filters to keep query latency low at scale.}
        \resumeItem{Designed real-time streaming pipelines using \textbf{WebSockets and MQTT} with retry and fallback handling, significantly reducing dropped-message incidents in production.}
        \resumeItem{Built \textbf{React.js + Redux} dashboards for AI analytics and production monitoring, improving observability and speeding up incident triage.}
    \resumeItemListEnd

\resumeSubheading
    {Full Stack Developer (Contract) -- PearlThoughts}{Feb 2025 -- Sep 2025}
    {Remote}{}
    \resumeItemListStart
        \resumeItem{Engineered backend automation systems using \textbf{NestJS, TypeScript, and Google Workspace APIs}, executing \textbf{1K+ workflows/day} across multiple client engagements.}
        \resumeItem{Developed APIs and microservices backed by \textbf{PostgreSQL} and \textbf{MongoDB}, replacing manual processing steps with automated workflows.}
        \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{AWS} with CI/CD pipelines for reliable, repeatable releases.}
        \resumeItem{Performed QA validation for Coursera course launches, auditing coding labs and grading systems to ensure stable student environments.}
    \resumeItemListEnd

\resumeSubheading
    {Full Stack Developer -- The DevOps Team}{Oct 2023 -- Jan 2025}
    {Bangalore, India}{}
    \resumeItemListStart
       \resumeItem{Optimized \textbf{Node.js + Express.js} APIs, cutting median response time from \textbf{800ms to 320ms} with \textbf{Redis caching} for high-frequency platform operations.}
       \resumeItem{Developed recommendation workflows for a job portal to improve candidate-job matching based on skills, preferences, and role requirements.}
        \resumeItem{Improved user onboarding conversion through A/B-tested \textbf{React.js and Next.js} signup and activation flows.}
        \resumeItem{Built analytics pipelines processing high-volume user event streams, supporting retention and engagement analysis.}
        \resumeItem{Implemented real-time notifications using \textbf{WebSockets} and automated deployments with \textbf{Docker and Kubernetes}.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
  {WorkBridge -- AI-Powered Project Collaboration Platform}
  {May 2026 -- Present}
  {React.js, Next.js, Node.js, Express.js, Python, PostgreSQL, Redis, OAuth $|$ \href{https://workbridgee.vercel.app/}{workbridgee.vercel.app}}
  \resumeItemListStart
    \resumeItem{Built and deployed an AI-powered collaboration platform that connects students with real-world industry projects through skill-based matching.}
    \resumeItem{Developed the full stack --- \textbf{React.js/Next.js} interfaces for project discovery and collaboration, with \textbf{Node.js, Express.js, and PostgreSQL} services for auth, project management, and workflows.}
    \resumeItem{Currently extending the platform with AI-based recommendation workflows to match student skills to project requirements. Additional projects, including RAG and agentic AI demos, on \href{https://github.com/maheshchichkoti}{\underline{GitHub}}.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-0.05in]
\item Oracle AI Vector Search Certified Professional, by \underline{\textcolor{blue}{\href{https://catalog-education.oracle.com/pls/certview/sharebadge?id=BBBFD68A8A08024E5624BE28AA84D101812885D8B9C036DA18F8F110A75CBB12}{Oracle}}} -- Sep 2025
\item Machine Learning I, by
     \underline{\textcolor{blue}{\href{https://badges.plus.columbia.edu/5fdeba5e-ee65-4041-86d9-602fb4d1f288\#acc.Xf1YuPmA}{Columbia University}}} -- Aug 2025
\item Oracle Cloud Infrastructure 2024 Generative AI Certified Professional, by
    \underline{\textcolor{blue}{\href{https://catalog-education.oracle.com/pls/certview/sharebadge?id=2FD55AA64EF5240AFF31F10E95EB6D46DCAC92326D8E2ABB457EE7AC8C3CAF65}{Oracle}}} -- Aug 2024
\item Java Full Stack Development Certificate, by Jspiders Bangalore -- Aug 2023
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Adichunchanagiri Institute of Technology}{Chikkamagaluru, KA}
      {Bachelor of Engineering, Visvesvaraya Technological University (VTU)}{Aug 2023}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
